
---
title: 'Testing UOD survey data'
author: "Sabbir Hassan"
output: github_document
   
---

```{r  echo=FALSE, results='hide',message=FALSE, warning=FALSE, fig.show='hide'}
#html_notebook: default
 #  word_document: default
  # pdf_document: default
library("R.methodsS3")
library("R.oo")
library("R.utils")
library("knitr")
library("rmarkdown")
library("markdown")
library("data.table")
library("ggplot2")
library("nCDunnett")
library("multcompView")
library("ggpubr")
library("PairedData")

```

# Understanding Our differences: Autism Survey Analysis

### Score Map Table:

```{r echo=FALSE, results = 'asis', message=FALSE}

rm(list=ls())

q_codes <- as.factor(c(rep("Q3a",3), rep("Q3b",3), rep("Q3c",3), rep("Q3d",3) ,rep("Q3e",3)))

questions <- as.factor(c(rep(c("People autism act same."), 3),rep(c("Brain affected by autism."), 3),rep(c("People autism strong interest in one topic."), 3),rep(c("Bright lights, loud noises don’t bother people autism."), 3),rep(c("People autism good at reading emotions."), 3)))

survey_data <- data.table(q_codes, questions)

survey_data$options <- as.factor(c("True","False","Don't Know","True","False","Don't Know","True","False","Don't Know","True","False","Don't Know","True","False","Don't Know"))

survey_data$scores <- as.integer(c(0,1,0,1,0,0,1,0,0,0,1,0,0,1,0))


#head(survey_data, n=05)

kable(survey_data)

#write.csv(survey_data, file = "C:\\Users\\sabbi\\Dropbox\\ProBono\\UOD\\UOD_Analysis\\output\\scoremap.csv")


```

### Figure 01

```{r echo=FALSE, results = 'show', message=FALSE}

viz_survey <- survey_data

ggplot(viz_survey, aes(x = as.factor(viz_survey$scores), y = scores, fill=options)) +
    geom_bar(position="dodge", stat="identity") +
    ggtitle("Assignment of Scores \n by Questions") +
    xlab("Questions") + 
    ylab("Score") +
    facet_grid( ~q_codes)
rm(viz_survey)

```




### Generating Table

Converting raw data table into long tables.

```{r echo=FALSE, results='hide',message=FALSE}

file_location <- "C:\\Users\\sabbi\\Dropbox\\ProBono\\UOD\\UOD_Analysis\\input\\rawdata.csv"
rawdata=read.csv(file_location, header =TRUE, na.strings=c("","N/A","NA"), 
                 stringsAsFactors = FALSE)

setDT(rawdata)
set.seed(100)
# Shuffling the dataset
rows <- sample(nrow(rawdata))
rawdata <- rawdata[rows, ]
rm(rows)

col_names_old <- names(rawdata)
setnames(rawdata, col_names_old[1:3], c("Schools","Student.Id","Subject.Id"))

rawdata$Schools <- as.factor(rawdata$Schools)
rawdata$Student.Id <- as.factor(rawdata$Student.Id)
rawdata$Subject.Id <- as.factor(rawdata$Subject.Id)

rawdata$Pre.Q.1 <- as.factor(rawdata$Pre.Q.1)
rawdata$Q4 <- as.factor(rawdata$Q4)
rawdata$Q5 <- as.factor(rawdata$Q5)


#kable(head(rawdata, n = 5))


```


```{r echo=FALSE, results='hide',message=FALSE}

clean.data <- na.omit(rawdata)

clean.data <- clean.data[, c("Pre.Q.1","Q4","Q5"):=NULL] 

idx1 = which(clean.data$Pre.Q3a==1)
idx2 = which(clean.data$Pre.Q3a==2)
idx3 = which(clean.data$Pre.Q3a==3)

clean.data$Pre.Q3a[idx1]=0
clean.data$Pre.Q3a[idx2]=2
clean.data$Pre.Q3a[idx3]=0


idx1 = which(clean.data$Post.Q3a==1)
idx2 = which(clean.data$Post.Q3a==2)
idx3 = which(clean.data$Post.Q3a==3)

clean.data$Post.Q3a[idx1]=0
clean.data$Post.Q3a[idx2]=2
clean.data$Post.Q3a[idx3]=0


idx1 = which(clean.data$Pre.Q3b==1)
idx2 = which(clean.data$Pre.Q3b==2)
idx3 = which(clean.data$Pre.Q3b==3)

clean.data$Pre.Q3b[idx1]=2
clean.data$Pre.Q3b[idx2]=0
clean.data$Pre.Q3b[idx3]=0

idx1 = which(clean.data$Post.Q3b==1)
idx2 = which(clean.data$Post.Q3b==2)
idx3 = which(clean.data$Post.Q3b==3)

clean.data$Post.Q3b[idx1]=2
clean.data$Post.Q3b[idx2]=0
clean.data$Post.Q3b[idx3]=0

idx1 = which(clean.data$Pre.Q3c==1)
idx2 = which(clean.data$Pre.Q3c==2)
idx3 = which(clean.data$Pre.Q3c==3)

clean.data$Pre.Q3c[idx1]=2
clean.data$Pre.Q3c[idx2]=0
clean.data$Pre.Q3c[idx3]=0

idx1 = which(clean.data$Post.Q3c==1)
idx2 = which(clean.data$Post.Q3c==2)
idx3 = which(clean.data$Post.Q3c==3)

clean.data$Post.Q3c[idx1]=2
clean.data$Post.Q3c[idx2]=0
clean.data$Post.Q3c[idx3]=0

idx1 = which(clean.data$Pre.Q3a==1)
idx2 = which(clean.data$Pre.Q3a==2)
idx3 = which(clean.data$Pre.Q3a==3)

clean.data$Pre.Q3d[idx1]=0
clean.data$Pre.Q3d[idx2]=2
clean.data$Pre.Q3d[idx3]=0


idx1 = which(clean.data$Post.Q3d==1)
idx2 = which(clean.data$Post.Q3d==2)
idx3 = which(clean.data$Post.Q3d==3)

clean.data$Post.Q3d[idx1]=0
clean.data$Post.Q3d[idx2]=2
clean.data$Post.Q3d[idx3]=0



idx1 = which(clean.data$Pre.Q3e==1)
idx2 = which(clean.data$Pre.Q3e==2)
idx3 = which(clean.data$Pre.Q3e==3)

clean.data$Pre.Q3e[idx1]=0
clean.data$Pre.Q3e[idx2]=2
clean.data$Pre.Q3e[idx3]=0


idx1 = which(clean.data$Post.Q3e==1)
idx2 = which(clean.data$Post.Q3e==2)
idx3 = which(clean.data$Post.Q3e==3)

clean.data$Post.Q3e[idx1]=0
clean.data$Post.Q3e[idx2]=2
clean.data$Post.Q3e[idx3]=0



#head(clean.data, n = 5)

rm(idx1)
rm(idx2)
rm(idx3)


```


```{r  echo=FALSE, results='hide',message=FALSE}
clean.data$PreScore <- apply(clean.data[,c(4:8)], 1, sum)
clean.data$PreScore <- (clean.data$PreScore/10)*100
clean.data$PostScore <- apply(clean.data[,c(9:13)], 1, sum)
clean.data$PostScore <- (clean.data$PostScore/10)*100


#kable(head(clean.data, n = 5))

```



```{r  echo=FALSE, results='show',message=FALSE}

newdata <- clean.data[,c("Subject.Id","Schools","PreScore","PostScore"),]

newdata_melted <- clean.data[,c("Subject.Id","Schools","PreScore","PostScore"),]

newdata_melted <- melt(newdata_melted,id.vars = c("Subject.Id","Schools"))


col_names_old <- names(newdata_melted)
setnames(newdata_melted, col_names_old[3:4], c("Tests","Scores"))

#head(newdata)
set.seed(20)
# Shuffling the dataset
rows <- sample(nrow(newdata_melted))
newdata_melted <- newdata_melted[rows, ]
rm(rows)


kable(head(newdata_melted, n=5))


```

```{r echo=FALSE, results='hide', message=FALSE}



```

### Figure 02:

```{r echo=FALSE, results='hide', message=FALSE}

viz_schools <- newdata_melted[, .(count = .N, Avg_Scores = mean(Scores)), by = c('Schools','Tests')]
#head(viz_schools, n=5)

ggplot(viz_schools, aes(x = Schools, y= count, fill=Schools)) +
    geom_bar(stat="identity") +
    ggtitle("Count of Students \n by Schools") +
    xlab("Schools") + 
    ylab("Count")


rm(viz_schools)

```

### Figure 03:

```{r  echo=FALSE, message=FALSE}

ggplot(newdata_melted, aes(x=Scores, fill=Tests)) + 
  geom_histogram(breaks=seq(0,100, by=20), 
                 col="blue") +
  ggtitle("Distribution of Pre & Post Scores \n (averaged by Schools)") +
  xlab("% Avg Scores") +
  ylab("Count")


#plot(newdata_melted$Scores[which((newdata_melted$Tests == "PreScore"))],newdata_melted$Scores[which((newdata_melted$Tests == "PostScore"))],xlab="Pre Scores", ylab="Post Scores")
```

### Figure 04:

```{r echo=FALSE, message=FALSE}

viz_schools <- newdata_melted[, .(count = .N, Avg_Scores = mean(Scores)), by = c('Schools','Tests')]
#head(viz_schools, n=5)

ggplot(viz_schools, aes(x = Schools, y = Avg_Scores,fill=Tests)) +
    geom_bar(position="dodge", stat="identity") +
    #geom_hline(yintercept=0.5, linetype="dashed", color = "blue", size=1) +
    ggtitle("Comparison of PreScore & PostScore \n by Schools") +
    xlab("Schools") + 
    ylab("% Avg Score")
rm(viz_schools)

```




```{r echo=FALSE, results='hide',message=FALSE}

clean.data2 <- na.omit(rawdata)
clean.data2 <- clean.data2[, c("Schools","Student.Id","Pre.Q.1","Q4","Q5"):=NULL] 

# ressiging pre-test data

clean.data2$Pre.Q3a[which(clean.data2$Pre.Q3a==1)]="T"
clean.data2$Pre.Q3a[which(clean.data2$Pre.Q3a==2)]="F"
clean.data2$Pre.Q3a[which(clean.data2$Pre.Q3a==3)]="DK"

clean.data2$Pre.Q3b[which(clean.data2$Pre.Q3b==1)]="T"
clean.data2$Pre.Q3b[which(clean.data2$Pre.Q3b==2)]="F"
clean.data2$Pre.Q3b[which(clean.data2$Pre.Q3b==3)]="DK"

clean.data2$Pre.Q3c[which(clean.data2$Pre.Q3c==1)]="T"
clean.data2$Pre.Q3c[which(clean.data2$Pre.Q3c==2)]="F"
clean.data2$Pre.Q3c[which(clean.data2$Pre.Q3c==3)]="DK"

clean.data2$Pre.Q3d[which(clean.data2$Pre.Q3d==1)]="T"
clean.data2$Pre.Q3d[which(clean.data2$Pre.Q3d==2)]="F"
clean.data2$Pre.Q3d[which(clean.data2$Pre.Q3d==3)]="DK"

clean.data2$Pre.Q3e[which(clean.data2$Pre.Q3e==1)]="T"
clean.data2$Pre.Q3e[which(clean.data2$Pre.Q3e==2)]="F"
clean.data2$Pre.Q3e[which(clean.data2$Pre.Q3e==3)]="DK"



# ressiging post-test data

clean.data2$Post.Q3a[which(clean.data2$Post.Q3a==1)]="T"
clean.data2$Post.Q3a[which(clean.data2$Post.Q3a==2)]="F"
clean.data2$Post.Q3a[which(clean.data2$Post.Q3a==3)]="DK"

clean.data2$Post.Q3b[which(clean.data2$Post.Q3b==1)]="T"
clean.data2$Post.Q3b[which(clean.data2$Post.Q3b==2)]="F"
clean.data2$Post.Q3b[which(clean.data2$Post.Q3b==3)]="DK"

clean.data2$Post.Q3c[which(clean.data2$Post.Q3c==1)]="T"
clean.data2$Post.Q3c[which(clean.data2$Post.Q3c==2)]="F"
clean.data2$Post.Q3c[which(clean.data2$Post.Q3c==3)]="DK"

clean.data2$Post.Q3d[which(clean.data2$Post.Q3d==1)]="T"
clean.data2$Post.Q3d[which(clean.data2$Post.Q3d==2)]="F"
clean.data2$Post.Q3d[which(clean.data2$Post.Q3d==3)]="DK"

clean.data2$Post.Q3e[which(clean.data2$Post.Q3e==1)]="T"
clean.data2$Post.Q3e[which(clean.data2$Post.Q3e==2)]="F"
clean.data2$Post.Q3e[which(clean.data2$Post.Q3e==3)]="DK"

clean.data2 <- data.table(clean.data2,stringsAsFactors=TRUE)

head(clean.data2, n = 5)



```


```{r echo=FALSE, results='hide', message=FALSE}

#clean.data2[, grepl("^Pre.", names(clean.data2)), with = FALSE]
col_names_old <- colnames(clean.data2)
col_names_old <- col_names_old[grepl("^Pre.|^Post.", col_names_old)]

d <- data.table(options=factor(), count=numeric(), tests=factor(), q_codes=factor())

#q <- "Pre.Q3b"

for (q in col_names_old) {
  #print(q)
  
  if (grepl("Pre.", q) == 1) {
    d2 <- clean.data2[, .(count = .N, tests = "Pre"), by = q]
    setnames(d2, c(q), c("options"))
    d2$q_codes <- c(rep(substr(q, (nchar("Pre.")+1), nchar(q)), 3))

  
  } else {
    d2 <- clean.data2[, .(count = .N, tests = "Post"), by = q]
    setnames(d2, c(q), c("options"))
    d2$q_codes <- c(rep(substr(q, (nchar("Post.")+1), nchar(q)), 3))

  
  }


  d <- rbind(d,d2) 
  
}

 d <- d[, .(tests = tests, percent = (count/sum(count))), by = c("options","q_codes")]
 

head(d, n = 05)

```


### Figure 05:

```{r echo=FALSE, message=FALSE}


ggplot(d, aes(x = options, y = percent, group = q_codes, fill = tests)) +
    geom_bar(position = "fill", stat = "identity") +
    #geom_text(aes(label = round(percent,2) ), position = position_stack(vjust = .5), color = "black", size = 2) +
    geom_hline(yintercept=0.5, linetype="dashed", color = "blue", size=1) +
    ggtitle("Comparison of Pre-test and Post-test options \n by Questions") +
    xlab("options") + 
    ylab("count") +
    facet_grid( ~ q_codes)
    
rm(d2)
rm(d)


```


```{r echo=FALSE, results='show', message=FALSE}


ggboxplot(newdata_melted, x = "Tests", y = "Scores", 
          color = "Tests", palette = c("blue", "red"),
          order = c("PreScore", "PostScore"),
          ylab = "Scores", xlab = "Tests")





```



```{r echo=FALSE, results='show', message=FALSE}

# Subset weight data before treatment
before <- subset(newdata_melted,  Tests == "PreScore", Scores,
                 drop = TRUE)
# subset weight data after treatment
after <- subset(newdata_melted,  Tests == "PostScore", Scores,
                 drop = TRUE)
# Plot paired data
#library(PairedData)
pd <- paired(before, after)
plot(pd, type = "profile")

rm(pd)
rm(before)
rm(after)

```

### Trying out paired t-tests

Assumption 1: Are the two samples paired?
Yes, since the data have been collected from suverying the same students twice before and after the intervention/program

Assumption 2: Is this a large sample?
N = 442 seems to be a large enough sample

Two dependent samples (within-subject design)

How to check the normality?
Use Shapiro-Wilk normality test as described at: Normality Test in R.

Null hypothesis: the data are normally distributed
Alternative hypothesis: the data are not normally distributed




```{r echo=FALSE, results='show', message=FALSE}



# Change density plot fill colors by groups
ggplot(newdata_melted, aes(x=Scores, fill=Tests)) +
  geom_density(alpha=0.6) 
  #geom_vline(newdata_melted, aes(xintercept=grp.mean, color=sex), linetype="dashed")




```


Null hypothesis: Mean difference between the pairs of observations is zero.
Alternative hypothesis: Mean difference between the pairs of observations is NOT zero.


```{r echo=FALSE, results='show', message=FALSE}

t.test(newdata$PostScore, newdata$PreScore, mu = 0, alt = "two.sided", paired = T, conf.level = 0.95)




```


### Trying out Wilcoxon signed-rank test

The paired samples Wilcoxon test (also known as Wilcoxon signed-rank test) is a non-parametric alternative to paired t-test used to compare paired data. It’s used when your data are not normally distributed.

Ass 01: each pair of samples are random and independent from the other observations. But not necessairy leaning each pre observation is independent of post observation

ass02: the distribution of the differences between the groups must be symmetrical

Null hypothesis: Median difference between the pairs of observations is zero.
Alternative hypothesis: Median difference between the pairs of observations is NOT zero.

```{r echo=FALSE, results='show', message=FALSE}

newdata$diff <- newdata$PostScore - newdata$PreScore

ggplot(newdata, aes(x=diff, fill = diff)) +
  geom_density(color="darkblue", fill="lightblue", alpha=0.6) +
  geom_vline(xintercept=median(newdata$diff), color="red", linetype="dashed")


```


```{r echo=FALSE, results='show', message=FALSE}

wilcox.test(newdata$PostScore, newdata$PreScore, alt = "two.sided", paired = T, conf.int = T, conf.level = 0.95, exact = F, correct = F)




```

